Fail Faster

### 2025-03-19 paper/paper.tex
wip etna

It is worth noting that the time-to-failure of a given strategy on a given seed is not necessarily representative of 
the strategy's average time-to-failure over a large number of trials. We normalize by computing relative performance (the ``speedup''). While this works in most cases,
it is not perfect.
For example, it is theoretically possible
to choose a seed such that the \textit{first} value produced by a generator discovers the bug, which would elide any differential speedup (and likewise
if both generators fail to find the bug).
To account for these cases, we repeat the above process over 10 seeds and compute the geometric average of their speedups.\footnote{Although the variance \textit{between} seeds in Etna can be vast, timing results are replicable for a \textit{given} seed. Across 1,000 trials using the same seed, 
the observed variance in time-to-failure was less than a nanosecond.}

\begin{figure}[h]
  \includegraphics[scale=0.333]{speedup.png}
  \caption{Geometric average of all speedups for each strategy and benchmark, showing that staging leads to better bug-finding ability across the board. As in \todo{earlier figure}, benchmarks with higher numbers of binds (BST (Single-Pass); STLC) see more benefit from staging, whereas benchmarks with more sampling (BST) see a greater speedup from \csplitmix.}
  \label{fig:etna}
\end{figure}

\begin{figure}[h]
  \includegraphics[scale=0.41]{swarm.png}
  \label{fig:swarm}
  \caption{Distribution of individual-task speedups across strategies and benchmarks. Extreme outliers correspond to large speedups.}
\end{figure}

>>>>

It is worth noting that the time-to-failure of a given strategy on a given seed is not necessarily representative of 
the strategy's average time-to-failure over a large number of trials. We normalize by computing relative performance, or the ``speedup''. While this works in most cases,
it is not perfect.
For example, it is theoretically possible
to choose a seed such that the \textit{first} value produced by a generator discovers the bug, which would elide any differential speedup (and likewise
if both generators fail to find the bug).
To account for these cases, we repeat the above process over 10 seeds.\footnote{Although the variance \textit{between} seeds in Etna can be vast, timing results are replicable for a \textit{given} seed. Across 1,000 trials using the same seed, 
the observed variance in time-to-failure was less than a nanosecond.}

The average of individual-task speedups for each strategy and benchmark, across all seeds, is shown in \figref{fig:etna}. Trends in bug-finding ability closely reproduce trends in performance from \secref{subsection:benchmarking}. The distribution of individual-task speedups, shown in \figref{fig:swarm}, tell a more interesting story: benchmarks

\begin{figure}[h]
  \includegraphics[scale=0.333]{speedup.png}
  \caption{Geometric average of all speedups for each strategy and benchmark, showing that staging leads to better bug-finding ability across the board.}
  \label{fig:etna}
\end{figure}

\begin{figure}[h]
  \includegraphics[scale=0.41]{swarm.png}
  \caption{Distribution of individual-task speedups across strategies and benchmarks. Extreme outliers correspond to large speedups.}
  \label{fig:swarm}
\end{figure}
